\documentclass{article}
\usepackage{geometry}
\usepackage{tcolorbox}
\geometry{a4paper, inner=3in,outer=3in, top=0.3in, bottom=0.3in}
\usepackage{decorule}
\pagestyle{empty}

\begin{document}
\centering
\newpage
\begin{tcolorbox}[height=26cm]
\centering
\huge\textsc{Characters of Infinite Jest}
\small
\vspace{0.3cm}
\decorule
\vspace{0.3cm}
\large\emph{The Incandenzas}
\small
\begin{itemize}
\item James Orin Incandenza\newline
\scriptsize{Filmmaker // Founder of E.T.A // Committed suicide in a microwave // Nicknames: Himself, The Mad Stork, The Sad Stork}
\item \small{Avril Incandenza (n\'{e}e Mondragon)}\newline
\scriptsize{James' Widow // Involved in running E.T.A. // Affiliated with the Militant Grammarians // Nickname: The Moms}
\item \small{Hal Incandenza}\newline
\scriptsize{Youngest Incandenza child // Protagonist // Student at E.T.A.}
\item  \small{Mario Incandenza}\newline
\scriptsize{Middle Incandenza child // Born with deformities // Filmmaker}
\item  \small{Orin Incandenza}\newline
\scriptsize {Oldest Incandenza child // Punter for the Arizona Cardinals // Serial womanizer // Cockroach killer}
\item  \small{Charles Tavis}\newline
\scriptsize{Head of E.T.A. // Avril`s half or adoptive brother
}
\end{itemize}
\vspace{0.1cm}
\large\emph{The Enfield Tennis Academy}
\small
\begin{itemize}
\item  \small{Michael Pemulis}\newline
\scriptsize{Hal's best friend // Prankster // Drug dealer //  Eschaton champion // Not destined for The Show}
\item  \small{John ``No Relation'' Wayne}\newline
\scriptsize{Top-ranked player at ETA // Discovered by James Incandenza during interviews of men named John Wayne for a film}
\item  \small{Eric Clipperton}\newline
\scriptsize{Won tennis matches by threatening to kill himself if he lost}
\item  \small{Other Prominent E.T.A. Students}\newline
\scriptsize{Ortho “The Darkness” Stice, Jim Troelsch, Trevor (“The Axhandle”) Axford, Ann Kittenplan, Ted Schacht, LaMont Chu, U.S.S. Millicent Kent}
Gerhardt Schtitt
\item  \small{Dr. Dolores Rusk}\newline
\scriptsize{Staff counselor at E.T.A. // In counseling sessions, just rephrases as a question the last thing said by the patient}
\item  \small{Lateral Alice Moore}\newline
\scriptsize{Member of the E.T.A. administrative staff}
\item \small{Cantrell}\newline
\scriptsize{Member of the E.T.A. administrative staff}
\item \small{Lyle}\newline
\scriptsize{Lives in the E.T.A. weight room and dispenses advice}
\end{itemize}
\vspace{0.1cm}
\end{tcolorbox}
\newpage
\begin{tcolorbox}[height=26cm]
\centering
\huge\textsc{Characters of Infinite Jest}
\small
\vspace{0.2cm}
\decorule
\vspace{0.2cm}
\large\emph{The Ennet House Drug and Alcohol Recovery House}
\small
\begin{itemize}
\item  \small{Don Gately}\newline
\scriptsize{Protagonist // Former thief // Demerol addict // Counselor in residence at the Ennet House}
\item  \small{Joelle Van Dyne}\newline
\scriptsize{Radio talkshow host // Former lover to Orin // Starred in many of James Incandenza films // Wears a veil // Nicknames: Madame Psychosis, P.G.O.A.T. (The Prettiest Girl of All Time)}
\item  \small{Kate Gompert}\newline
\scriptsize{Cannabinoid addict // Suffers from extreme unipolar depression}
\item  \small{Pat Montesian}\newline
\scriptsize{The Ennet House manager}
\item  \small{Ken Erdedy}\newline
\scriptsize{Cannabinoid addict}
\item  \small{Bruce Green}\newline
\scriptsize{Ex-husband of Mildred Bonk-Green}
\item  \small{Tiny Ewell}\newline
\scriptsize{A lawyer with dwarfism // Obsessed with tattoos}
\end{itemize}
\vspace{0.1cm}
\large\emph{The Detectives}
\small
\begin{itemize}
\item  \small{Hugh Steeply (a.k.a. Helen Steeply)}\newline
\scriptsize{Agent for O.U.S. // Currently in disguise as a female reporter profiling Orin}
\item  \small{Remy Marathe}\newline
\scriptsize {Member of the A.F.R. (separatists) // Quadruple-agent who secretly talks to Hugh Steeply}
\item  \small{M. Fortier}\newline
\scriptsize{Marathe's superior}
\end{itemize}
\vspace{0.1cm}
\large\emph{Other}
\small
\begin{itemize}
\item  \small{Johnny Gentle}\newline
\scriptsize{Famous crooner // Former singer // Leader of C.U.S.P. // President of the United States // Responsible for O.N.A.N. // Responsible for Great Con(cav|vex)ity // Responsible for subsidized time // Germaphobe
}
\item  \small{Rodney P. Tine}\newline
\scriptsize{Chief of the O.U.S. // Chief and part of (or adviser to) the Gentle administration}
\item  \small{Poor Tony Krause}\newline
\scriptsize{Almost killed by Drano-spiked heroin // Accidentally steals a woman`s artificial heart // Has a seizure while in withdrawal // Nickname: P.T. Krause}
\item  \small{Stavros Lobokulas}\newline
\scriptsize{Gately's partner in cleaning the Shattuck Shelter}
\end{itemize}





\end{tcolorbox}


\newpage
\begin{tcolorbox}[height=25.5cm]
\centering
\huge\textsc{Common Acronyms of Infinite Jest}
\small
\vspace{0.2cm}
\decorule
\vspace{0.2cm}
\begin{flushleft}
\textbf{A.F.R.} - Les Assassins des Fauteuils Rollents (The Wheelchair Assassins)
\vspace{0.1cm}
\newline
\emph{Qu\'{e}b\'{e}cois extremist separatist group. Developed after the United States coerced Canada and Mexico into joining O.N.A.N. Wants Canada to secede from O.N.A.N.}
\newline

\textbf{A.A./N.A.} - Alcoholics Anonymous / Narcotics Anonymous
\vspace{0.1cm}
\newline
\emph{Program followed in Ennet House. }
\newline

\textbf{B.S.} - Before Subsidization
\vspace{0.1cm}
\newline
\emph{Before the years were sponsored by companies. Last year B.S. 2001.}
\newline

\textbf{C.U.S.P.}  - Clean U. S. Party
\vspace{0.1cm}
\newline
\emph{Johnny Gentle's pro-hygiene political platform.}
\newline

\textbf{E.M.P.H.H.} - Enfield Marine Public Health Hospital complex
\vspace{0.1cm}
\newline
\emph{AKA Enfield Marine VA Hospital Complex. Managed by U.S. Veteran's Administration.}
\newline

\textbf{E.T.A.} - Enfield Tennis Academy
\vspace{0.1cm}
\newline
\emph{Boarding school in Enfield, MA. Tennis Academy for talented players. Hal Incandenza is a student, James Incandenza was the director.}
\newline

\textbf{O.N.A.N.} - Organization of North American Nations
\vspace{0.1cm}
\newline
\emph{A unified North American superstate. President Johnny Gentle. United States coerced Canada and Mexico into joining.}
\newline

\textbf{O.U.S./U.S.O.U.S/B.S.S.} - United States Office of Unspecified Services / Bureau des Services sans Sp\'{e}cificit\'{e} 
\vspace{0.1cm}
\newline
\emph{Government spy agency. Hugh Steeply works for them.}
\newline




\end{flushleft}
\end{tcolorbox}
\begin{tcolorbox}[height=25.5cm]
\vspace{0.1cm}

\textbf{O.N.A.N.T.A.} - Organization of North American Nations Tennis Association
\vspace{0.1cm}
\newline
\emph{Urine testing, Toxologist.}
\newline

\textbf{T.P.} - Teleputer
\vspace{0.1cm}
\newline
\emph{AKA TP. Combination television/VCR/computer/videophone. Entertainment device.}
\newline

\textbf{U.H.I.D.} - Union of the Hideously and Improbably Deformed
\vspace{0.1cm}
\newline
\emph{Agnostic-style 12-step support-group for people. Joelle Van Dyne becomes a member.}
\newline

\textbf{W.Y.Y.Y.} - Radio station
\vspace{0.1cm}
\newline
\emph{Radio station found on FM-109. From MIT in Cambridge, MA. Madame Psychosis has a talk show.}

\centering
\vspace{0.2cm}
\rule{\textwidth}{1pt}\newline
\vspace{0.2cm}
\newline
\huge\textsc{Chronology of Infinite Jest}
\small
\vspace{0.1cm}
\decorule
\vspace{0.1cm}
\begin{flushleft}
\begin{enumerate}
\item Before Subsidization
\item Year of the Whopper 
\item Year of the Tucks Medicated Pad
\item Year of the Trial Size Dove Bar 
\item Year of the Perdue Wonderchicken
\item Year of the Whisper-Quiet Maytag Dishmaster
\item Year of the Yushityu 2007 Mimetic-Resolution-Cartridge-View-Motherboard-Easy-To-Install-Upgrade For Infernatron / InterLace TP Systems For Home, Office Or Mobile [sic]
\item Year of Dairy Products from the American Heartland
\item Year of the Depend Adult Undergarment
\item Year of Glad
\end{enumerate}
\end{flushleft}
\end{tcolorbox}

\end{document}
